---
title: "What qualities are correlated with a high grossing film?"
author: "Ryan Harrington"
date: "3/28/2022"
output:
  html_document:
    theme: yeti
    highlight: textmate
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

```{r}
library(tidyverse)
```

# Reading your data

```{r}
movies <- read_csv("Data_Transformations/movies_clean.csv")
```
```{r}
# View(movies)
```

```{r}
summary(movies)
```

```{r}
str(movies)
```

```{r}
glimpse(movies)
```

# Select

```{r}
select(movies, id, original_title, budget, popularity)
```

```{r}
select(movies, -keywords)
```

```{r}
select(movies, id, original_title, genre_Action:genre_TV)
```

```{r}
select(movies, id, original_title, starts_with("genre"))
```

## Creating the `movies_sel` dataset

* id
* contain "title"
* original_language
* budget
* contains "vote"
* starts with "release"
* is a double
* starts with "genre"

```{r}
movies_sel <-
  select(movies, 
         id, contains("title"), contains("original"), budget, contains("vote"),
         starts_with("release"), where(is.double), starts_with("genre"))
```

# `filter`

```{r}
glimpse(movies_sel)
```
Which movies are action movies?

```{r}
filter(movies_sel,
       genre_Action)
```

What movies have a vote average over 7.5?

```{r}
filter(movies_sel,
       vote_average > 7.5)
```
What action movies have an average voter rating over 7.5?

```{r}
filter(movies_sel, 
       genre_Action, 
       vote_average > 7.5)
```
How many movies have an original language in English, French, Spanish, or Italian?
"en", "fr", "es", "it"

```{r}
filter(movies_sel,
       original_language == "en" | original_language == "fr" | original_language == "es" | original_language == "it")
```

Given the numbers 1 through 100, which of those numbers are in 1 through 10?

```{r}
1:100 %in% 1:10
```

```{r}
filter(movies_sel,
       original_language %in% c("en", "fr", "es", "it"))
```

```{r}
romance_languages <- c("en", "fr", "es", "it", "po")

filter(movies_sel,
       original_language %in% romance_languages)
```

# `arrange`

What movie is most expensive to produce? Which movie has the highest budget?

```{r}
arrange(movies_sel,
        desc(budget))
```
```{r}
arrange(movies_sel,
        release_year, desc(budget))
```

# `mutate`

What movie has the highest profit?

```{r}
mutate(movies_sel,
       profit = revenue - budget)
```
How does the runtime for each movie compare to the average runtime for all movies?

```{r}
mutate(movies_sel,
       runtime_diff = runtime - mean(runtime, na.rm = TRUE),
       budget_diff = budget - mean(budget, na.rm = TRUE))
```

# `summarize`

What is the median and mean budget for all movies?

```{r}
summarize(movies_sel,
          budget_median = median(budget, na.rm = TRUE),
          budget_mean = mean(budget, na.rm = TRUE))
```
# `group_by` / `ungroup`

What was the average budget by release year?

```{r}
movies_group <- 
  group_by(movies_sel,
           release_year)
```

```{r}
summarize(movies_group,
          budget_median = median(budget, na.rm = TRUE),
          budget_mean = mean(budget, na.rm = TRUE))
```

What movie released in 2001 had the highest budget?

```{r}
movies_selected <- select(movies, id, original_title, budget, release_year)
movies_filtered <- filter(movies_selected, release_year == 2001)
arrange(movies_filtered, desc(budget))
```

# Piping `%>%`

```{r}
movies_sel %>% 
  select(id, original_title, budget, release_year) %>% 
  filter(release_year == 2001) %>% 
  arrange(desc(budget))
```
```{r}
movies_sel %>% select(id)
```
What movie had the highest vote average overall?

* select
* mutate
* filter
* arrange
* summarize
* group_by / ungroup


```{r}
movies_sel %>% 
  arrange(desc(vote_average))
```

```{r}
movies_sel %>% 
  filter(vote_average == max(vote_average))
```

What movie had the highest vote average for movies released after 2010?

```{r}
movies_sel %>% 
  filter(release_year > 2010) %>% 
  arrange(desc(vote_average))
```

What movie had the highest vote average for movies with a vote counter greater than the median released after 2010?

```{r}
movies_sel %>% 
  filter(release_year > 2010,
         vote_count > median(vote_count, na.rm = TRUE)) %>% 
  arrange(desc(vote_average))
```

What movie had the highest vote average for movies that made at least double of their budget?

```{r}
movies %>% 
  filter(budget > 0) %>% 
  mutate(budget_double = budget * 2) %>% 
  filter(revenue >= budget_double) %>% 
  arrange(desc(vote_average))
```

```{r}
movies %>% 
  filter(budget > 0) %>% 
  mutate(revenue_percent = (revenue - budget) / budget) %>% 
  filter(revenue_percent >= 2) %>% 
  arrange(desc(vote_average))
```

How many movies are represented from each language?

```{r}
movies_sel %>% 
  group_by(original_language) %>% 
  summarize(count = n()) %>% 
  ungroup() %>% 
  arrange(desc(count))
```

```{r}
movies_sel %>% 
  count(original_language, sort = T, name = "count")
```

How much total budget was used across each original language?

```{r}
movies_sel %>% 
  group_by(original_language) %>% 
  summarize(budget_total = sum(budget)) %>% 
  ungroup() %>% 
  arrange(desc(budget_total))
```

How did vote averages change for English language films over time?

```{r}
movies_english_over_time <- 
  movies_sel %>% 
  filter(original_language == "en") %>% 
  group_by(release_year) %>% 
  summarize(vote_average = mean(vote_average)) %>% 
  ungroup()


movies_english_over_time %>% 
  ggplot(aes(x = release_year,
             y = vote_average)) + 
  geom_point()
```

How many movie titles match their original title? How many did not?

```{r}
movies_sel %>% 
  mutate(title_match_flag = title == original_title) %>% 
  count(title_match_flag) %>% 
  ggplot(aes(x = n,
             y = title_match_flag)) +
  geom_col()
```

```{r}
movies_sel %>% 
  mutate(title_match_flag = title == original_title) %>% 
  count(release_year, title_match_flag)
```

What was the highest budget movie by release year?

```{r}
movies_sel %>% 
  group_by(release_year) %>% 
  filter(budget == max(budget)) %>% 
  ungroup() %>% 
  select(release_year, budget, title) %>% 
  arrange(release_year)
```

```{r, eval = FALSE}
library(tidyverse)
movies_sel_sample <- 
  structure(list(id = c(19995, 285, 206647, 49026, 49529, 559), 
                 title = c("Avatar", "Pirates of the Caribbean: At World's End", 
                           "Spectre", "The Dark Knight Rises", "John Carter", "Spider-Man 3"
                 ), original_language = c("en", "en", "en", "en", "en", "en"
                 ), vote_average = c(7.2, 6.9, 6.3, 7.6, 6.1, 5.9)), row.names = c(NA, 
                                                                                   -6L), class = c("tbl_df", "tbl", "data.frame"))

movies_sel_sample %>% 
  group_by(original_language) %>% 
  summarize(vote_average = mean(vote_average, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(x = vote_average,
             y = original_language)) %>% 
  geom_col()
```

